### 2023-02-20 chapter3/chapter3.tex
Modified end of introduction to chapter 3 to reflect inclusion of only the training tutorial

The tutorials are available alongside the source code for these packages and will likely continue to undergo revisions and expansions. They are, however, adapted from their current form in the following sections. Though the tutorials are largely independent of the others, here they are presented in their intended order. The first two are brief introductions to the MixMod and Homomorph APIs, respectively. The next discusses a generalization of HMMs called autoregressive HMMs (ARHMMs). The final tutorial covers methods for training HMMs. As each is a self-contained document with an introduction and conclusion, they are presented without further commentary.

>>>>

The tutorials are available alongside the source code for these packages on GitHub. Though each is largely independent of the others, they follow a logical progression. For example, both Mixmod and Homomorph have tutorials which serve as brief introductions to the theory, applications, and APIs for their respective models. Homomorph then has two additional tutorials. The first discusses a generalization of HMMs called autoregressive HMMs (ARHMMs), and the second covers methods for training HMMs. For brevity, only the training tutorial is adapted from its current form in the following section. As the tutorial is a self-contained document with an introduction and conclusion, it is presented without further commentary.
